Statistical Theory\\ Chess Dataset Analysis

### 2024-09-30 Article/Article.tex
Updated Article

\subsection{Gamma-Poisson distribution}

>>>>

\subsection{Gamma-Poisson distribution}
The GP distribution is a simple average between a general Gamma distribution(GGD) and a Poisson distribution weighted by a parameter w.
\[f_{GP}(x|\alpha, \beta, \gamma, \lambda, w) = wf_{GGD}(x|\alpha, \beta, \gamma) + (1-w)f_P(\lambda)\]
Let us find the MLE of GP:
\[L_{GP}(\alpha, \beta, \gamma, \lambda, w) = \prod_{i=1}^n f_{GP}(x_i|\alpha, \beta, \gamma, \lambda, w)\]
\[= \prod_{i=1}^n [wf_{GGD}(x|\alpha, \beta, \gamma) + (1-w)f_P(\lambda)]\]
Now, by taking the negative log of the likelihood function, we can use minimizing optimization algorithms to find the optimal parameters numerically, since here an analytical solution is difficult to find.
